---
title: "Working with APIs"
author: "Locke Data"
date: "14 May 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# APIs

## What is an API?
An Application Programming Interface (API) is a way to provide instructions to an applications using code.

This saves having to use websites and manually perform actions.

## Interfaces
Each API should have an **endpoint**, which a unique URL it can be accessed from. Then additional parameters can be provided to provide options to the API.

## Verbs
APIs are designed to work with actions.

- **GET** is used to retrieve info
- **POST** is used to insert info (or provide secret data)
- **PUT** is used to insert info
- **PATCH** is used to update info
- **DELETE** is used to remove info

# httr

## httr
httr is a package designed to make consuming APIs easier.

## Simple httr

httr has verbs ...

```{r}
library(httr)
httr::GET("https://google.co.uk")
```

## Simple httr

Get response info ...
```{r}
goog<-httr::GET("https://google.co.uk")
status_code(goog)
headers(goog)
```

## Simple httr

Get content...
```{r}
content(goog)
```